Mulit-view 3D Aerosol Distribution Recovery

### 2013-07-27 article.tex
bookmark

\title{Sky Tomography for 3D Aerosol Distribution Recovery}

@@

\begin{abstract}
  Aerosols effect climate, health and aviation.  Currently, their
  retrieval assumes a plane-parallel atmosphere and solely vertical
  radiative transfer (RT). We propose a principle to recover the atmosphere
  as it really is: a three dimensional (3D), volumetric, transparent
  huge object. Tomography is the key to recovery. The process involves
  acquiring the sky lightfield by multi-view wide-angle photography on
  a very large scale. The tomography model is distinct, as the light
  source is unidirectional and uncontrolled, while off-axis scattering
  dominates the images.  We formulate an image formation model based
  on 3D RT. Model inversion is done using optimization
  methods, exploiting a closed-form gradient which we derive for the
  model-fit cost function. The problem is complex but tractable and
  parallelizable, eventually estimating the 3D aerosol distribution.
\end{abstract}

@@

Lightfield and integral imaging~\cite{bishop,horstmeyer,kim,Ng1948}
samples the optical radiance distribution in location and
direction. It is mainly used in small-scale setups. This paper deals
with a huge scale, up to Earth's size.  The atmosphere allows light to
pass through in multiple locations and directions. Light is affected
by this medium. Therefore, in this paper we lay out a principle to
recover this 3D medium using measured and modeled lightfields
(Fig.~\ref{fig:groundgrid}).
\begin{figure*}[t!]
  \begin{center}
    \yoavcomment{\includegraphics[width=\linewidth]{images/groundtomog24.pdf}}
  \end{center}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras.}
  \label{fig:groundgrid}
\end{figure*}
Projecting this large object to various directions is similar to
tomography in other scientific domains. However, the formulation here
is distinct. Most tomography setups have a controlled and/or
multidirectional radiation source~\cite{gorbunov,messer}. In contrast,
our source is the uncontrolled, unidirectional Sun. Moreover, typical
tomography relies on a linear model~\cite{gregson}: the pixel value is
a linear combination of components along a line of sight (LOS), or a
multiplicative combination (linearized by a logarithm). Linear
tomography can detect volcanic gas~\cite{wright}, which absorbs
UV. Other gases in the atmosphere absorb IR. However, in visible
light, atmospheric attenuation is typically dominated by {\em
  scattering} by particles (aerosols), rather than absorption by
gasses. Thus, in our problem, we cannot rely on direct illumination,
but on sunlight scattered into the LOS.  The model turns out to be
{\em nonlinear, yet tractable}.

We do not deal with clouds here. Clouds scatter sunlight very strongly
and are easily observed. Hence they are directly recovered using
common stereoscopic tools, similarly to opaque surfaces~\cite{seiz}.
On the other hand, aerosols have much more subtle visual effects and
are thus more difficult to recover. We focus on them.  In remote
sensing~\cite{diner}, imaging through air is associated with {\em
  atmospheric correction}, based on {\em aerosol retrieval}. In this
discipline, the atmosphere is often assumed to be plane-parallel, for
simplicity, using only 1D vertical RT. Consequently
state-of-the-art aerosol retrieval is done in distinct large lateral
blocks~\cite{Martonchikc} with limited height
resolution~\cite{kalashnikova}. We, however, seek high resolution 3D
recovery. Computational photography offers new ways to peer into
media. In addition to active descattering~\cite{fuchs,kim,Ng1948} and
recovery of refractive transparent objects~\cite{ihrke}, overcoming
the atmosphere~\cite{Joshi2010,Zhu2013} to view ground objects was
studied in horizontal, fixed
views~\cite{fattal,he,Chen,kratz,narasimhan2,oakley,Hschechner2,tan}. In
this paper, however, the medium itself, at all relevant altitudes is
the object of interest.

3D recovery of this medium has direct implications to various
scientific communities that either rely on remotely-sensed imagery,
study the atmosphere, or overcome the medium to see beyond. These
include meteorology, atmospheric sciences, volcanology, and
climatology.  Aerosol retrieval is important for understanding climate
evolution~\cite{Dayan2008,kalashnikova} and monitoring air
quality. Mapping aerosol density is significant to aviation safety,
which needs real time assessment of conditions and visibility around
flight paths. To keep safe, today's coarse sensing limits flight
capacity. A prominent example is the 2010 eruption of Iceland's
Eyjafjallaj$\ddot {\rm o}$kull volcano, whose ash (aerosols) covered
much of Europe's airspace, grounding $\approx 100,000$
flights. Knowing the 3D distribution of aerosol density may indicate
safe 3D corridors to safely pass through, enhancing airspace
use. Viewing beyond the medium, atmospheric correction is needed, for
example, in satellite tracking of chlorophyll
distributions~\cite{johnsen}. Additional bodies in the solar system
have atmospheres. These objects can be viewed from multiple directions
by probes.  The approach described here may be helpful there.

We model passive optical tomographic imaging of 3D atmospheric
scatterer distributions in cloudless conditions. Then, we solve this
tomography problem, to recover the distribution. Recovery is
formulated as an optimization that minimizes a cost function. We
derive the gradient of this cost function, to enable efficient
optimization.

\section{Related Work}
\label{sec:literature}

{\em Lightfield}, or {\em integral}
imaging~\cite{Ng2006,bishop,Ng1948}, samples the radiance distribution
in location and direction. It has so far been used in small-scale
setups. Our proposed research deals with huge scale, up to Earth's
size. Capturing the lightfield in very large scales requires uncommon
sensors. Sampling Earth both spatially and angularly is done by the
Multiangle Imaging SpectroRadiometer (MISR)~\cite{Martonchikc} from
space, the Airborne Multiangle SpectroPolarimetric
Imager (AirMSPI)~\cite{dinerDavis10}, and other spaceborne and
airborne instruments.

Dehazing strives to improve quality of images taken through a
semi-transparent medium, be it murky liquid~\cite{kim,fuchs},
haze~\cite{fattal,Hschechner2}, or fog~\cite{narasimhan2}.  In remote
sensing~\cite{kokhan}, imaging through air is associated with {\em
  atmospheric correction}, based on {\em aerosol retrieval}.  In this
methods the medium is usually assumed to be uniform or at least
plane-parallel.  We, however, seek 3D recovery.  Another major
difference is that these methods see the translucent medium as a
disturbance that algorithms need to overcome, while in our research it
is the medium that we want to recover.

Computed Tomography (CT) refers to the reconstruction of a 3D object
from a collection of projections of the object using any kind of
penetrating radiation. CT finds wide use in medical imaging but is
also valuable in other scientific fields, like
geophysics~\cite{Kazahaya2008}, material science~\cite{Baruchel2000},
astrophysics, and more.  Imaging of gaseous materials is also the
target of extensive CT research~\cite{Price2001,Cosofret2009}. CT is
based on an image formation model that describes the physical process
underlying the projected measurements.  Most image formation models
assume either absorption or emission processes. Other image formation
models assume dominant diffusion by scattering~\cite{Boas2001}.

CT uses several different methods for reconstructing the underlying
medium. Transform algorithms are based on the Fourier and Radon
transforms. Both relate the projection (or its Fourier transform) to
the medium (or its Fourier transform). Solving for the medium involves
calculating the inverse transform in an iterative process.  These
algorithms assume a linear image formation model and require large
amount of projections to give reasonable results. The simultaneous
algebraic reconstruction technique
(SART)~\cite{KakAvinashC.andSlaney2001} is another common method which
is used when the image formation model is too big for explicit matrix
representation. Stochastic Tomography~\cite{gregson} uses a different
approach where the reconstruction is done in the space of projections
using a probabilistic process based on random walk. This bypasses the
need to discretize the signal, usually represented over a grid, and
the use of large matrices to represent the formation model.

Our research topic is closely related to optical
tomography~\cite{Arridge}. Optical tomography uses light to visualize
tissue, usually from close range.  Due to the highly scattering nature
of biological tissue, optical tomography uses diffusive approximation
in the image formation model.  Another method, based on scattering, is
the X-Ray Scatter CT~\cite{Aviles2011} which measures the absorption
and scattering coefficients of the medium separately.

However, the formulation of our problem is {\em different} than prior
situations. Most tomography setups have a controlled and/or
multidirectional radiation source~\cite{messer}. In contrast, our
source is the uncontrolled, unidirectional Sun. Moreover, typical
tomography relies on a linear model: the pixel value is a linear
combination of components along a line of sight (LOS), or a
multiplicative combination which is linearized by a logarithm.
However, photographs of the atmosphere are a mixture of {\em
  scattering}, and absorption. The model turns out to be {\em
  nonlinear, yet tractable}.

>>>>

\title{Mulit-view 3D Aerosol Distribution Recovery}

@@

\begin{abstract}
  Aerosols effect climate, health and aviation.  Currently, their
  retrieval assumes a plane-parallel atmosphere and solely vertical
  radiative transfer (RT). We propose a principle to estimate the aerosol  
  distribution as it really is: a three dimensional (3D) volume, using visible light. 
  The principle is a type of tomography. The process involves
  wide angle integral imaging of the sky on a very large scale.  
  We formulate an image formation model based
  on 3D RT. Model inversion is done using optimization
  methods, exploiting a closed-form gradient which we derive for the
  model-fit cost function.  The tomography model is distinct, as the radiation
  source is unidirectional and uncontrolled, while off-axis scattering
  dominates the images.  
\end{abstract}

@@

Optical lightfield and integral imaging~\cite{bishop,horstmeyer,kim,Ng1948}
samples the optical radiance distribution in location and
direction. It is mainly used in small-scale setups. This paper deals
with a far larger scale, to estimate scatterer 3D spatial distribution in the sky. 
The atmosphere allows light to pass through in multiple locations and directions. Light is affected
by this medium. Therefore, in this paper we lay out a principle to
recover this 3D distribution using measured and modeled light-fields
(Fig.~\ref{fig:groundgrid}).
\begin{figure*}[t!]
  \begin{center}
    \yoavcomment{\includegraphics[width=\linewidth]{images/groundtomog24.pdf}}
  \end{center}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras.}
  \label{fig:groundgrid}
\end{figure*}
3D recovery of this medium has direct implications to various
scientific communities that either rely on remotely-sensed imagery,
study the atmosphere, or overcome the medium to see beyond. These
include meteorology, atmospheric sciences, volcanology, and
climatology.  Aerosol retrieval is important for understanding climate
evolution~\cite{Dayan2008,kalashnikova} and monitoring air
quality. Mapping aerosol density is significant to aviation safety,
which needs real time assessment of conditions and visibility around
flight paths.

In remote sensing~\cite{diner}, imaging through air is associated with {\em
  atmospheric correction}, based on {\em aerosol retrieval}. In this
discipline, the atmosphere is often assumed to be plane-parallel, using one-dimensional vertical RT. Consequently state-of-the-art aerosol retrieval is done in distinct large lateral
blocks~\cite{Martonchikc} with limited height
resolution~\cite{kalashnikova}. We, however, seek 3D
recovery. Atmospheric correction is related to dehazing~\cite{Joshi2010,Zhu2013}. In
this paper, however, the medium itself, at all relevant altitudes is the object of interest.

We rely on sky imaging from multiple directions and locations. Such projection is similar to
tomography in other scientific domains~\cite{Arridge}. However, the situation here
is distinct. Most tomography setups have a controlled and/or
multidirectional radiation source~\cite{Boas2001,messer}. In contrast,
our source is the uncontrolled, unidirectional Sun. Moreover, typical
tomography relies on a linear model~\cite{gregson}: the pixel value is
a linear combination of components along a line of sight (LOS), or a
multiplicative combination (linearized by a logarithm). Linear
tomography can detect gases~\cite{Kazahaya2008,Price2001,Cosofret2009,wright}, which absorb
UV or IR radiation. However, aerosol attenuation of visible
light is typically dominated by {\em scattering}, rather than absorption. Since the radiation source is single and fixed in space and time, we cannot rely on direct illumination for tomographic recovery of attenuation fields~\cite{Aviles2011}. We may only use sunlight scattered into the LOS. The model is
{\em nonlinear, yet tractable}. We model passive optical tomographic imaging of 3D atmospheric
scatterer distributions in cloudless conditions. Then, we solve this
tomography problem, to recover the distribution. Recovery is
formulated as an optimization that minimizes a cost function. We
derive the gradient of this cost function, to enable efficient
optimization.
